---
title: "Data Exploration"
output:
  html_document:
    df_print: paged
---

Load R libraries
```{r}
library(Amelia)
library(mice)
library(miceadds)
library(ggplot2)
library(lattice)
```

## Impute Training Dataset

Load vehicle training dataset without missing target.
```{r}
setwd("/Users/davidleonardi/Projects/KE5107_BayesianNetworks/")
training_data <- read.csv("./Data/vehicle_safety_training_data.csv")
training_data$GV_LANES <- as.factor(training_data$GV_LANES)
training_data$GV_MODELYR <- as.factor(training_data$GV_MODELYR)
training_data$GV_WGTCDTR <- as.factor(training_data$GV_WGTCDTR)
training_data$OA_BAGDEPLY <- as.factor(training_data$OA_BAGDEPLY)
training_data$OA_MAIS <- as.factor(training_data$OA_MAIS)
training_data$OA_MANUSE <- as.factor(training_data$OA_MANUSE)
training_data$OA_SEX <- as.factor(training_data$OA_SEX)
training_data$VE_GAD1 <- as.factor(training_data$VE_GAD1)

summary(training_data)
```

Show missing data in diagram.
```{r}
missmap(training_data[-1], col=c('grey', 'steelblue'), y.cex=0.5, x.cex=0.8)
```

Get hard numbers of missing data.
```{r}
# Let's also get some hard numbers
sort(sapply(training_data, function(x) { sum(is.na(x)) }), decreasing=TRUE)
```

Show missing data pattern.
```{r}
md.pattern(training_data)
```

Use mice with Decision Tree to impute missing data.
```{r}
imp.data <- mice(training_data, m=1, method='cart', printFlag=FALSE)
summary(imp.data)
```

Write imputted values from decision tree model.
```{r}
# write results
write.mice.imputation(mi.res=imp.data, name="mice_imp_cart")
```

Compare it with Mean value.
```{r}
imp.data_raw_mean <- mice(training_data, m=1, defaultMethod=c('mean', 'cart', 'cart', 'cart'), printFlag=FALSE)
summary(imp.data_raw_mean)
```

Write imputted mean values from mean model.
```{r}
# write results
write.mice.imputation(mi.res=imp.data_raw_mean, name="mice_imp_mean" )
```

Plot GV_DVLAT and VE_PDOF_TR for imputed data using Decision Tree.
```{r}
xyplot(imp.data, GV_DVLAT ~ VE_PDOF_TR)
```

Plot GV_DVLONG and VE_PDOF_TR for imputed data using Decision Tree.
```{r}
xyplot(imp.data, GV_DVLONG ~ VE_PDOF_TR)
```

Plot GV_DVLAT and GV_FOOTPRINT for imputed data using Decision Tree.
```{r}
xyplot(imp.data, GV_DVLAT ~ GV_FOOTPRINT)
```

Plot GV_DVLAT and GV_FOOTPRINT for imputed data using Decision Tree.
```{r}
xyplot(imp.data, GV_DVLONG ~ GV_FOOTPRINT)
```

Plot GV_DVLAT and VE_PDOF_TR for imputed data using Mean value.
```{r}
xyplot(imp.data_raw_mean, GV_DVLAT ~ VE_PDOF_TR)
```

Plot GV_DVLONG and VE_PDOF_TR for imputed data using Mean value.
```{r}
xyplot(imp.data_raw_mean, GV_DVLONG ~ VE_PDOF_TR)
```

Plot GV_DVLAT and GV_FOOTPRINT for imputed data using Mean value.
```{r}
xyplot(imp.data_raw_mean, GV_DVLAT ~ GV_FOOTPRINT)
```

Plot GV_DVLONG and GV_FOOTPRINT for imputed data using Mean value.
```{r}
xyplot(imp.data_raw_mean, GV_DVLONG ~ GV_FOOTPRINT)
```

Save the imputed data.
```{r}
data_complete <- complete(imp.data)
write.csv(data_complete, "./Data/vehicle_safety_training_imputed_data.csv")
```

## Impute Testing Dataset

Load vehicle testing dataset without missing target.
```{r}
testing_data <- read.csv("./Data/vehicle_safety_testing_data.csv")
testing_data$GV_LANES <- as.factor(testing_data$GV_LANES)
testing_data$GV_MODELYR <- as.factor(testing_data$GV_MODELYR)
testing_data$GV_WGTCDTR <- as.factor(testing_data$GV_WGTCDTR)
testing_data$OA_BAGDEPLY <- as.factor(testing_data$OA_BAGDEPLY)
testing_data$OA_MAIS <- as.factor(testing_data$OA_MAIS)
testing_data$OA_MANUSE <- as.factor(testing_data$OA_MANUSE)
testing_data$OA_SEX <- as.factor(testing_data$OA_SEX)
testing_data$VE_GAD1 <- as.factor(testing_data$VE_GAD1)

summary(testing_data)
```

Use mice with Decision Tree to impute missing data.
```{r}
imp.data <- mice(testing_data, m=1, method='cart', printFlag=FALSE)
summary(imp.data)
```

Save the imputed data.
```{r}
testing_data_complete <- complete(imp.data)
write.csv(testing_data_complete, "./Data/vehicle_safety_testing_imputed_data.csv")
```
