Load R libraries
```{r}
library(Amelia)
library(mice)
library(ggplot2)
library(lattice)
```

Load vehicle data without missing target.
```{r}
setwd("/Users/davidleonardi/Projects/KE5107_BayesianNetworks/")
data <- read.csv("./vehicle_safety_remove_missing_target.csv")
data$GV_LANES <- as.factor(data$GV_LANES)
data$GV_MODELYR <- as.factor(data$GV_MODELYR)
data$GV_WGTCDTR <- as.factor(data$GV_WGTCDTR)
data$OA_BAGDEPLY <- as.factor(data$OA_BAGDEPLY)
data$OA_MAIS <- as.factor(data$OA_MAIS)
data$OA_MANUSE <- as.factor(data$OA_MANUSE)
data$OA_SEX <- as.factor(data$OA_SEX)
data$VE_GAD1 <- as.factor(data$VE_GAD1)

summary(data)
```

Show missing data in diagram.
```{r}
missmap(data[-1], col=c('grey', 'steelblue'), y.cex=0.5, x.cex=0.8)
```

Get hard numbers of missing data.
```{r}
# Let's also get some hard numbers
sort(sapply(data, function(x) { sum(is.na(x)) }), decreasing=TRUE)
```

Show missing data pattern.
```{r}
md.pattern(data)
```

Use mice with Decision Tree to impute missing data.
```{r}
imp.data <- mice(data, m=1, method='cart', printFlag=FALSE)
summary(imp.data)
```

Compare it with Mean value.
```{r}
imp.data_raw_mean <- mice(data, m=1, defaultMethod=c('mean', 'cart', 'cart', 'cart'), printFlag=FALSE)
summary(imp.data_raw_mean)
```

Plot GV_DVLAT and VE_PDOF_TR for imputed data using Decision Tree.
```{r}
xyplot(imp.data, GV_DVLAT ~ VE_PDOF_TR)
```

Plot GV_DVLONG and VE_PDOF_TR for imputed data using Decision Tree.
```{r}
xyplot(imp.data, GV_DVLONG ~ VE_PDOF_TR)
```

Plot GV_DVLAT and GV_FOOTPRINT for imputed data using Decision Tree.
```{r}
xyplot(imp.data, GV_DVLAT ~ GV_FOOTPRINT)
```

Plot GV_DVLAT and GV_FOOTPRINT for imputed data using Decision Tree.
```{r}
xyplot(imp.data, GV_DVLONG ~ GV_FOOTPRINT)
```

Plot GV_DVLAT and VE_PDOF_TR for imputed data using Mean value.
```{r}
xyplot(imp.data_raw_mean, GV_DVLAT ~ VE_PDOF_TR)
```

Plot GV_DVLONG and VE_PDOF_TR for imputed data using Mean value.
```{r}
xyplot(imp.data_raw_mean, GV_DVLONG ~ VE_PDOF_TR)
```

Plot GV_DVLAT and GV_FOOTPRINT for imputed data using Mean value.
```{r}
xyplot(imp.data_raw_mean, GV_DVLAT ~ GV_FOOTPRINT)
```

Plot GV_DVLONG and GV_FOOTPRINT for imputed data using Mean value.
```{r}
xyplot(imp.data_raw_mean, GV_DVLONG ~ GV_FOOTPRINT)
```

Save the imputed data.
```{r}
data_complete <- complete(imp.data)
write.csv(data_complete, "./vehicle_safety_imputed_data.csv")
```
